---
title: "Figure_1"
author: "Mike O'Donnell"
date: "9/6/2017"
output:
  html_document:
    code_folding: hide
    fig_height: 5
    fig_width: 7
    theme: flatly
  pdf_document:
    always_allow_html: yes
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
pathname = getwd()
library(magrittr)
library(knitr)
library(dplyr)
library(ggplot2)
library(ggbeeswarm)
library(beeswarm)
library(ggthemes)
library(viridis)
library(lme4)
library(schoRsch)
library(DHARMa)
library(multcomp)
library(tidyr)
library(rstanarm)
library(ggrepel)
library(rstan)
library(rstanarm)
library(MASS)
devtools::install_github("mikeod38/dauergut")
library(dauergut)

dauer_ANOVA <- . %>% lm(data = ., formula = pct ~ genotype)
```


#__Intestinal mTORC2 signaling alters sensory driven traits__{.tabset}

##__Fig 1 Intestinal mTORC2 prevents dauer formation__{.tabset}

###1B 
```{r TORC2 data load}
strains<-c("N2", "rict-1(mg360)", "rict-1(ft7)", "sgk-1(ok538)", "akt-1(mg306)", "akt-2", "pkc-2")
foods <- "OP50"

TORC2<-read.csv(file.path(pathname, "data/1B_rict-1_TORC2.csv"), header=TRUE) %>% dauergut::format_dauer(p.dauer = "non") #including partial/pd as non-dauer due to excess zeros. 

lm <- TORC2 %>% dauer_ANOVA()
#stan
stan.glmm <- TORC2 %>% dauergut::run_dauer_stan()
```

```{r plot TORC2}
contrasts<-dauergut::dunnett_contrasts(lm, ref.index = 1, "genotype")
mixed<-dauergut::getStan_CIs(stan.glmm, type = "dauer")
plot.contrasts<-c("",contrasts$prange[1:6])

(p<-dauergut::plot_CIs(TORC2, title='mTORC2 prevents high temperature dauer formation', plot.contrasts, ypos = 1.075, type = "dauer"))
```
1B. mTORC2 controls high temperature-induced dauer formation. Animals were grown 60hrs post egg lay at 27º, proportion of dauers in each strain is shown. Arrested L3 and/or partial/post dauers are included as non-dauers due to excess arrest in _rict-1(ft7)_. Increased dauer formation occurs in mTORC2-specific _rict-1_ mutants, as well as in mutants of mTORC2 targets _sgk-1_ and _akt-1_. Box and scatter plot show raw data. Bayesian 95% (grey) and 75% (thick-grey) credible intervals are shown on the right (see methods). All p-values reflect ANOVA with Dunnett post-hoc comparision to N2. n≥5 experiments over 3 independent days.

`r knitr::kable(contrasts)`

###1C

```{r gut rescue data}
strains<-c("N2","rict-1(mg360)",
           "rict-1(mg360); ex[ges1]",
           "rict-1(mg360); ex[gpa4]",
           "rict-1(ft7)",
           "rict-1(ft7); ex[ges1]",
           "rict-1(ft7); ex[elt2]",
           "rict-1(ft7); ex[ifb2]",
           "sgk-1(ok538)",
           "sgk-1(ok538); ex[ges1]",
           "akt-1(mg306)",
           "akt-1(mg306); ex[ges1]")
foods = "OP50"

gutresc<-read.csv(file.path(pathname, "data", "1C_ges-1_rescue_rict_sgk.csv")) %>% dauergut::format_dauer(p.dauer = "non") %>% 
  mutate(allele = factor(allele, levels = c("WT","mg360","ft7","ok538","mg306")))

gutresc %<>% dplyr::mutate(adj.pct = case_when(.$pct == 0 ~ 0.01, .$pct == 1 ~ 0.99, TRUE ~ .$pct))

lm <- gutresc %>% dauer_ANOVA()
stan.glmm <- gutresc %>% dauergut::run_dauer_stan()


```

```{r gut resc plot, fig.width=6, fig.height=3}
contrasts<-dauergut::tukey_contrasts(lm, "genotype") 
mixed<-stan.glmm %>% dauergut::getStan_CIs(type="dauer")
plot.contrasts<-c("",contrasts$prange[1], "", "", contrasts$prange[4], "","","", contrasts$prange[8],"",contrasts$prange[10],"")
plot.contrasts.2<-c("", "",contrasts$prange[12:13],"",contrasts$prange[39:41],"", contrasts$prange[61],"", contrasts$prange[66])

(p<-dauergut::plot_CIs(gutresc, title='mTORC2 components act in the intestine to regulate 
dauer formation', plot.contrasts, plot.contrasts.2=plot.contrasts.2, ypos = 1.075,type = "dauer", offset = 0))
```

1C. mTORC2 acts in the intestine to inhibit high-temperature dauer formation. Animals were grown 60hrs post egg lay at 27º, proportion of dauers in each strain is shown. Increased dauer formation of _rict-1_ and _sgk-1_ mutants is rescued by intestinal-specific expression. _akt-1_ mutants were not rescued using this promoter. Box and scatter plot show raw data. Bayesian 90% (grey) and 50% (red) credible intervals are shown on the right (see methods). All p-values reflect ANOVA with Dunnett post-hoc comparision to N2. p-values in red indicate rescue comparisons to respective control mutants. n≥6 experiments over 3 independent days.

`r knitr::kable(contrasts)`
